Exploration

### 2018-03-10 exploration.Rmd
added extra plots, fixed plot objects that had changed

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
mean_abund <- 100
regPlots <- F
ipmPlots <- F
nPlots <- 5
z.rng <- c(1, 12)
n <- 10  # ncells in IPM matrix
tmax <- 30
cells <- 1:n_distinct(lc.df$CellID)
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-1.75, .75), # b1 + b2*z
                    s_x=c(2, -.1, -2, -.1, 2, -2, -.4), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(2, -.1, 2, -.1, 2, -2), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2
                    fl_x=c(2, -.1, -2, -.1, 1, 1), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, -1, -.1, .2), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.03, # p(establishment)
                    NDD=T, # negative density dependence: p_est=p_est/N
                    NDD_n=100, # mean number of recruits if NDD
                    rcr_SB=0.5, # p(recruit from seedbank)
                    rcr_dir=0.5, # p(recruit directly)
                    s_SB=0.3, # p(survive in seedbank additional year)
                    sdd_max=5, # max SDD distance in cells
                    sdd_rate=1 # SDD dispersal rate
                    ))
sp_i$p$p_emig <- pexp(0.5, sp_i$p$sdd_rate, lower.tail=F) # p(seed emigrates)
```

@@

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage & IPM matrix objects
p <- sp_i$p
setup_IPM_matrix(n, z.rng, buffer=0.5, discrete=1)
IPMs <- Ps <- Fs <- Fb <- array(0, dim=c(n+1, n+1, n.cell))
Nt <- array(dim=c(n+1, n+1, n.cell, tmax))
d <- sdd.j <- vector("list", length=n.cell)
B <- cbind(rpois(n.cell, n_i), matrix(0, nrow=n.cell, ncol=tmax))
nSd <- D <- p_est.i <- matrix(nrow=n.cell, ncol=tmax)
lam.t <- p_est.t <- matrix(nrow=n.cell, ncol=tmax-1)
sdd <- array(0, dim=dim(sdd.pr) + c(0,0,1,0)) # add layer for nEmig
sdd[,,1:2,] <- sdd.pr

@@

#---- Realization: generate simulated data
## local growth
for(i in 1:n.cell) {
  d[[i]] <- data.frame(yr=1, size=runif(n=n_i[i], min=z.rng[1], max=z.rng[2]))
  E <- sim_expected(d[[i]], p, map(X, ~(.[i,])), n_z)
  d[[i]] <- sim_realized(d[[i]], 1:nrow(d[[i]]), E, p, lo, hi)
  nSd[i,1] <- sum(d[[i]]$seed, na.rm=T)
  sdd[,,3,i] <- nSd[i,1] * p$p_emig * sdd[,,1,i]
}
## dispersal & density dependence
for(i in 1:n.cell) {
  D[i,1] <- sum(sdd[,,3,][sdd.j[[i]]])
  p_est.i[i,1] <- ifelse(p$NDD, min(p$NDD_n/(nSd[i,1]+D[i,1]),p$p_est), p$p_est)
  d[[i]] <- sim_recruits(d[[i]], p_est.i[i,1], nSd[i,1], B[i,1], D[i,1], p)
  B[i,2] <- sim_seedbank(nSd[i,1], B[i,1], D[i,1], p)
}
## iterate forward
for(k in 2:tmax) {
  for(i in 1:n.cell) {
    size.k <- d[[i]]$sizeNext[!is.na(d[[i]]$sizeNext) & d[[i]]$yr == k-1]
    if(length(size.k) > 0) {
      k.index <- (1:length(size.k)) + nrow(d[[i]])
      d[[i]][k.index, "size"] <- size.k
      d[[i]][k.index, "yr"] <- k
      E <- sim_expected(d[[i]][k.index,], p, map(X, ~(.[i,])), n_z)
      d[[i]] <- sim_realized(d[[i]], k.index, E, p, lo, hi)
      nSd[i,k] <- sum(d[[i]]$seed[k.index], na.rm=T)
    } else {
      nSd[i,k] <- 0
    }
    sdd[,,3,i] <- nSd[i,k] * p$p_emig * sdd[,,1,i]
  }
  for(i in 1:n.cell) {
    D[i,k] <- sum(sdd[,,3,][sdd.j[[i]]])
    p_est.i[i,k] <- ifelse(p$NDD, min(p$NDD_n/(nSd[i,k]+D[i,k]),p$p_est), p$p_est)
    d[[i]] <- sim_recruits(d[[i]], p_est.i[i,k], nSd[i,k], B[i,k], D[i,k], p)
    B[i,k+1] <- sim_seedbank(nSd[i,k], B[i,k], D[i,k], p)
  }
}

lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
lam.df %<>% 
  add_column(nSeed=nSd[,tmax], B0=B[,1], Btmax=B[,tmax+1], D=D[,tmax], 
             N=map_dbl(d, ~sum(!is.na(.$sizeNext[.$yr==tmax]))),
             N.surv=map_dbl(d, ~sum(.$surv[.$yr==tmax], na.rm=T)),
             N.rcr=map_dbl(d, ~sum(is.na(.$size[.$yr==tmax])))) %>%
  mutate(nSdStay=nSeed*(1-p$p_emig), nSdLeave=nSeed*p$p_emig) %>%
  add_column(Ntmax=apply(Nt[,,,tmax],3,sum), lam.tmax=lam.t[tmax-1,])

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lam.tmax))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(Ntmax)*(Ntmax>10))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=1)
ggplot(lam.df, aes(x=lon, y=lat, fill=lambda>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=lam.tmax>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=Ntmax>1)) + geom_tile() 
ggplot(lam.df, aes(x=lon, y=lat, fill=Ntmax>1 & lam.tmax<1)) + geom_tile() 
ggplot(lam.df, aes(x=lon, y=lat, fill=log(N))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(N.surv))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(N.rcr))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=nSeed)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=Btmax)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D + nSdStay)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=Btmax>B0)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay/D)) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=1)
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay < D & lambda < 1)) +
  geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOpn, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)

sample.cells <- sample.int(n.cell, nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
  mx <- cbind(1, as.matrix(xx))
  xxx <- seq(0, hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
    w1 <- Re(eigen(IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(mx[,2], antilogit(mx[,1:n_sz]%*%p$s_z + c(X_s[i,]%*%p$s_x)), col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(mx[,2], mx[,1:n_gz]%*%p$g_z + c(X_g[i,]%*%p$g_x), col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(mx[,2], antilogit(mx[,1:n_flz]%*%p$fl_z + c(X_fl[i,]%*%p$fl_x)),
            col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(mx[,2], exp(mx[,1:n_seedz]%*%p$seed_z + c(X_seed[i,]%*%p$seed_x)),
            col=2)
    plot(y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(d[[i]]$sizeNext[is.na(d[[i]]$size)], col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, y)
  for(i in sample.cells) {
    z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
    z.t$y <- y[findInterval(z.t$size, y, all.inside=T)]
    totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
    image.plot(x, x, t(Ps[,,i]), main=paste("P matrix:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,1/(n_i[i]^.25)))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(x, x, t(Fs[,,i]), main=paste("F matrix:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*hi*.9)
    image.plot(x, x, t(sens(IPMs[,,i])), main=paste("Sensitivity:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
    image.plot(x, x, t(elas(IPMs[,,i])), main=paste("Elasticity:", main.i),
               xlab="Size (t)", ylab="Size (t+1)")
  }
}
image.plot(x, x, t(apply(Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, t(apply(Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, sens(t(apply(IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
```

>>>>

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
mean_abund <- 500
regPlots <- T
ipmPlots <- T
nPlots <- 5
z.rng <- c(1, 12)
n <- 50  # ncells in IPM matrix
tmax <- 30
cells <- 1:n_distinct(lc.df$CellID)
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-8, 2.1, -.09), # b1 + b2*z + b3*z^2
                    s_x=c(2, -.1, -2, -.1, 2, -2, -.4), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(2, -.1, 2, -.1, 2, -2), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2
                    fl_x=c(-2, -.1, -2, -.1, 1, 1), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, -1, -.1, .2), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.03, # p(establishment)
                    NDD=T, # negative density dependence: p_est=p_est/N
                    NDD_n=100, # mean number of recruits if NDD
                    rcr_SB=0.5, # p(recruit from seedbank)
                    rcr_dir=0.5, # p(recruit directly)
                    s_SB=0.3, # p(survive in seedbank additional year)
                    sdd_max=5, # max SDD distance in cells
                    sdd_rate=1 # SDD dispersal rate
                    ))
sp_i$p$p_emig <- pexp(0.5, sp_i$p$sdd_rate, lower.tail=F) # p(seed emigrates)
```

@@

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage & IPM matrix objects
p <- sp_i$p
setup_IPM_matrix(n, z.rng, buffer=0.5, discrete=1)
IPMs <- Ps <- Fs <- Fb <- array(0, dim=c(n+1, n+1, n.cell))
Nt <- array(dim=c(n+1, n+1, n.cell, tmax))
d <- sdd.j <- vector("list", length=n.cell)
B <- cbind(rpois(n.cell, n_i), matrix(0, nrow=n.cell, ncol=tmax))
nSd <- D <- p_est.i <- N_sim <- matrix(0, nrow=n.cell, ncol=tmax)
lam.t <- p_est.t <- matrix(nrow=n.cell, ncol=tmax-1)
sdd <- array(0, dim=dim(sdd.pr) + c(0,0,1,0)) # add layer for nEmig
sdd[,,1:2,] <- sdd.pr

@@

#---- Realization: generate simulated data
## local growth
for(i in 1:n.cell) {
  d[[i]] <- data.frame(yr=1, size=runif(n=n_i[i], min=z.rng[1], max=z.rng[2]))
  E <- sim_expected(d[[i]], p, map(X, ~(.[i,])), n_z)
  d[[i]] <- sim_realized(d[[i]], 1:nrow(d[[i]]), E, p, lo, hi)
  nSd[i,1] <- sum(d[[i]]$seed, na.rm=T)
  sdd[,,3,i] <- nSd[i,1] * p$p_emig * sdd[,,1,i]
}
N_sim[,1] <- n_i
## dispersal & density dependence
for(i in 1:n.cell) {
  D[i,1] <- sum(sdd[,,3,][sdd.j[[i]]])
  p_est.i[i,1] <- ifelse(p$NDD, min(p$NDD_n/(nSd[i,1]+D[i,1]),p$p_est), p$p_est)
  d[[i]] <- sim_recruits(d[[i]], p_est.i[i,1], nSd[i,1], B[i,1], D[i,1], p)
  B[i,2] <- sim_seedbank(nSd[i,1], B[i,1], D[i,1], p)
}
## iterate forward
for(k in 2:tmax) {
  for(i in 1:n.cell) {
    size.k <- d[[i]]$sizeNext[!is.na(d[[i]]$sizeNext) & d[[i]]$yr == k-1]
    if(length(size.k) > 0) {
      k.index <- (1:length(size.k)) + nrow(d[[i]])
      d[[i]][k.index, "size"] <- size.k
      d[[i]][k.index, "yr"] <- k
      E <- sim_expected(d[[i]][k.index,], p, map(X, ~(.[i,])), n_z)
      d[[i]] <- sim_realized(d[[i]], k.index, E, p, lo, hi)
      nSd[i,k] <- sum(d[[i]]$seed[k.index], na.rm=T)
      N_sim[i,k] <- length(size.k)
    }
    sdd[,,3,i] <- nSd[i,k] * p$p_emig * sdd[,,1,i]
  }
  for(i in 1:n.cell) {
    D[i,k] <- sum(sdd[,,3,][sdd.j[[i]]])
    p_est.i[i,k] <- ifelse(p$NDD, min(p$NDD_n/(nSd[i,k]+D[i,k]),p$p_est), p$p_est)
    d[[i]] <- sim_recruits(d[[i]], p_est.i[i,k], nSd[i,k], B[i,k], D[i,k], p)
    B[i,k+1] <- sim_seedbank(nSd[i,k], B[i,k], D[i,k], p)
  }
}

lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
lam.df %<>% 
  add_column(nSeed=nSd[,tmax], B0=B[,1], Btmax=B[,tmax+1], D=D[,tmax], 
             N=map_dbl(d, ~sum(!is.na(.$sizeNext[.$yr==tmax]))),
             N.surv=map_dbl(d, ~sum(.$surv[.$yr==tmax], na.rm=T)),
             N.rcr=map_dbl(d, ~sum(is.na(.$size[.$yr==tmax])))) %>%
  mutate(nSdStay=nSeed*(1-p$p_emig), nSdLeave=nSeed*p$p_emig) %>%
  add_column(Ntmax=apply(Nt[,,,tmax],3,sum), lam.tmax=lam.t[,tmax-1])

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lam.tmax))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(Ntmax)*(Ntmax>10))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=1)
ggplot(lam.df, aes(x=lon, y=lat, fill=lambda>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=N>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=lam.tmax>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=Ntmax>1)) + geom_tile() 
ggplot(lam.df, aes(x=lon, y=lat, fill=Ntmax>1 & lam.tmax<1)) + geom_tile() 
ggplot(lam.df, aes(x=lon, y=lat, fill=log(N))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(N.surv))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=log(N.rcr))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=nSeed)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D + nSdStay)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=Btmax)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=Btmax>B0)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay/D)) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=1)
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay < D & lambda < 1)) +
  geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOpn, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)
matplot(t(log(lam.t)), type="l", lty=1, col=rgb(0,0,0,0.1))
matplot(t(log(apply(Nt, 3:4, sum))), type="l", lty=1, col=rgb(0,0,0,0.1))
matplot(t(N_sim[,2:tmax]/N_sim[,1:(tmax-1)]), type="l", lty=1, col=rgb(0,0,0,.1))
matplot(t(log(N_sim+1)), type="l", lty=1, col=rgb(0,0,0,0.1))
#matplot(t(log(nSd*(1-p$p_emig)+D)), type="l", lty=1, col=rgb(0,0,0,0.1))

sample.cells <- sample((1:n.cell)[lam.df$N.surv>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
  mx <- cbind(1, as.matrix(xx))
  xxx <- seq(0, hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- d[[i]][!is.na(d[[i]]$size) & d[[i]]$yr==tmax,]
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(mx[,2], antilogit(mx[,1:n_z$s]%*%p$s_z + c(X$s[i,]%*%p$s_x)), col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(mx[,2], mx[,1:n_z$g]%*%p$g_z + c(X$g[i,]%*%p$g_x), col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(mx[,2], antilogit(mx[,1:n_z$fl]%*%p$fl_z + c(X$fl[i,]%*%p$fl_x)),
            col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(mx[,2], exp(mx[,1:n_z$seed]%*%p$seed_z + c(X$seed[i,]%*%p$seed_x)),
            col=2)
    plot(y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(d[[i]]$sizeNext[is.na(d[[i]]$size)], col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, y)
  for(i in sample.cells) {
   z.t <- d[[i]][!is.na(d[[i]]$size) & d[[i]]$yr==tmax,] 
   main.i <- paste("Cell", i)
   z.t$y <- y[findInterval(z.t$size, y, all.inside=T)]
   totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,1/(n_i[i]^.25)))
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*hi*.9)
   image.plot(x, x, t(sens(IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
  }
}
image.plot(x, x, t(apply(Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, t(apply(Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, sens(t(apply(IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
```
